---
title: ' How well do people exercise? '
output: html_document
---
##Name: Parnian Zargham

## Executive Summary

In this project the goal is to predict how well people exercise from data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways.

## Preprocessing the data
The first step is to load the data using the provided URL,and remove “#DIV/0!”, replace with an NA value.. 

```{r}
urltrain<-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
urltest<-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
trainData1<-read.csv(urltrain,na.strings=c("NA","#DIV/0!", ""))
testData1<-read.csv(urltest,na.strings=c("NA","#DIV/0!", ""))
```
We nead to laod the required library for this study.
```{r}
library(caret)
library(kernlab)
library(randomForest)
```
Some of the data in this datasets are missing,so we need to remove them first.Moreover, the first 7 columns of the data are irrelavant data to our predicition,so we need to remove those,too.

```{r}
# Delete columns with all missing values
trainData2<-trainData1[,colSums(is.na(trainData1)) == 0]
testData2 <-testData1[,colSums(is.na(testData1)) == 0]

# remove irrelavant comulum
trainData  <-trainData2[,-(1:7)]
testData <-testData2 [,-(1:7)]
```

## Cross-Validation
In this study we divide the data to two groups: training data( 75% of dataset) to define the model and testing data(25% of dataset) to validate our model. 
```{r}
set.seed(13343)
inTrain<- createDataPartition(trainData$classe,p=.75,list=FALSE)
training<-trainData[inTrain,]
testing<-trainData[-inTrain,]


dim(training)
dim(testing)
```

## Modeling
In this part we chose random forest becuase of it's good preformance in classification problems.Which you can see here it has 100% accuracy here(confusionMatrix result). The expected out-of-sample error is calculated as 1 - accuracy,as you see form the confusionmatrix result is 0.

```{r}
#Model
model <- randomForest(classe~.,data=training,method="class")

pred<-predict(model,training)

# if you get an error install.packages("e1071")

confusionMatrix(pred,training$classe)
```

## Result
Our prediction model was performed on the test data with 20 observation and here is the results:
```{r}
predtest <- predict(model,testData , type="class")
predtest
```